---
title: "p8105_hw5_WZ2591"
author: "Wenyu Zhang"
date: "11/15/2021"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
## import and clean data

```{r}
homicide_df = 
  read_csv("data-homicides-master/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ",", collapse = NULL), 
    resolved_cases = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved")
    ) %>% 
  filter(city_state != "Tulsa,AL") %>% 
  select(city_state, resolved_cases)
  

homicide_df
```

## summarize within cities to obtain the total number of homicides and the number of unsolved homicides

```{r}
number_homicides_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    cases_total = n(),
    unsolved_cases_total = sum(resolved_cases == "unsolved")
  )

number_homicides_df
```

## use prop.test function to estimate the proportion of homicides that are unsolved

```{r}
prop.test(
  number_homicides_df %>% filter(city_state == "Baltimore,MD") %>% pull(unsolved_cases_total), 
  number_homicides_df %>% filter(city_state == "Baltimore,MD") %>% 
    pull(cases_total)
  ) %>% 
  broom::tidy()
```

## run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each.

```{r}
results_df = 
  number_homicides_df %>% 
  mutate(
    prop_tests = map2(.x = unsolved_cases_total, .y = cases_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

results_df
```

```{r}
results_df_plot = 
  results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

results_df_plot
```

# Probelm 2
```{r, results='hide', message=FALSE}
data_df = 
  tibble(
    file_name = list.files("lda-data")
  ) %>% 
  mutate(
    path = str_c("lda-data/", file_name),
    data = map(path, read_csv)
  )
```

## 1. Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time

```{r}
lda_tidy_df = 
  data_df %>% 
  unnest(data) %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation_values") %>% 
  separate(file_name, into = c("arm", "subject_ID"), sep = "_") %>% 
  mutate(
    arm = str_replace(arm, "con", "Control"),
    arm = str_replace(arm, "exp", "Experimental"),
    subject_ID = str_replace(subject_ID, ".csv", ""),
    week = str_replace(week, "week_", "")) %>% 
  mutate(arm = as.factor(arm)) %>% 
  select(-path)
```

## 2. Tidy the result; manipulate file names to include control arm and subject ID

```{r}
lda_control_df = 
  lda_tidy_df %>%
  filter(arm == "Control")
```

## 3. Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
lda_tidy_plot = 
  lda_tidy_df %>% 
  ggplot(aes(x = week, 
             y = observation_values , 
             group = subject_ID, 
             color = subject_ID)) +
  geom_line() +
  facet_grid(. ~ arm) +
  labs(
    title = "observations of control group and experimental group over time",
    x = "Weeks",
    y = "Observation values",
    caption = "the data was loaded from longitudinal study"
  ) + 
  scale_color_hue(name = "subject_ID", h = c(10, 300))

lda_tidy_plot  
```

Based on the graphs above, the experimental graph shows that values positively increase as the week increases.  The control group shows that there is no obviously relationship between observation values and week date because values show random change over weeks

# Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
filling_missing = function(x) {
  if (is.numeric(x)) {
    x = replace_na(x,round(mean(x, na.rm = TRUE), digits = 1))
  } else if (is.character(x)) {
    x = replace_na(x, "virginica")
  }
}
```

```{r}
filled_data = 
  map(iris_with_missing, filling_missing) %>%
  as_tibble()

filled_data
```